---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
h7 {
  font-size: 12px;
}
h8 {
  font-size: 12px;
}
```

```{r, results="asis"}
---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
h7 {
  font-size: 12px;
}
h8 {
  font-size: 12px;
}
```

```{r, results="asis"}
cat("#### level_4 {.tabset}\n\n")
cat("hi from level 4\n\n")
for(i in 1:3){
  cat("##### level_5", i, "{.tabset}\n\n")
  cat("hi from level 5", i, "\n\n")
  for(j in 1:3){
    cat("###### level_6", j, "{.tabset}\n\n")
    cat("hi from level 6", j, "\n\n")
    for(k in 1:3){
#     cat("####### level_7", k, "{.tabset}\n\n")
      cat('<div id="level_7-', i, '-', j, '-', k, '" class="section level7 tabset">', sep="")
      cat('<h7>level_7 1</h7>')
      cat("hi from level 7", i, j, k, "\n\n")
#      cat("######## level_8_1\n\n")
      cat('<div id="level_8-', i, '-', j, '-', k, '-1" class="section level8">', sep="")
      cat('<h8>level_8 1</h8>')
      cat("hi from level 8_1", i, j, k, "\n\n")
      cat("</div>\n\n")  # closes '<h8>level_8 1</h8>'
#      cat("######## level_8_2\n\n")
      cat('<div id="level_8-', i, '-', j, '-', k, '-2" class="section level8">', sep="")
      cat("hi from level 8_2", i, j, k, "\n\n")
      cat('<h8>level_8 2</h8>')
      cat("</div>\n\n")  # closes '<h8>level_8 2</h8>'
      cat("</div>\n\n")  # closes '<h7>level_7</h7>'
    }
  }
}
```
